---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
```

## Load the data


```{r load data}
activity <- read.csv("activity.csv")
```

# What is mean total number of steps taken per day?

## Remove NAs and calculate
```{r 1}
activity_r <- activity[!is.na(activity$steps),]
sum_result <- tapply(activity_r$steps, factor(activity_r$date),FUN = sum)
hist(sum_result, xlab = "number of steps")
average <- mean(sum_result)
med <- median(sum_result)
```
The mean of total number of steps taken per day is `r average`, median is `r med`.  

# What is the average daily activity pattern?
```{r 2}
daily_mean_result <- tapply(activity_r$steps, factor(activity_r$interval),FUN = mean)
plot(c(1:dim(daily_mean_result)),daily_mean_result,
xlab = "time interval index",
ylab = "steps",
type = "l")
max_loc <- which(daily_mean_result == max(daily_mean_result))
```
The maximun time period is `r max_loc

# Imputing missing values

```{r 3}
sum(is.na(activity$steps))
im_activity <- activity
for (i in c(1:NROW(im_activity$steps)) ){
        if (is.na(im_activity$steps[i])){
                id <- ((im_activity$interval[i])%/%100)*12+(((im_activity$interval[i]))%%100)/5+1
                im_activity$steps[i] <- daily_mean_result[id]
        }
                
}
sum_im_result <- tapply(im_activity$steps, factor(im_activity$date),FUN = sum)
hist(sum_im_result, xlab = "number of steps")
average_im <- mean(sum_im_result)
med_im <- median(sum_im_result)
```
The mean of total number of steps taken per day is `r average_im`, median is `r med`.  
The result is different. 10000-15000 interval increased by 8 days. The interval where is the mean
stays in will increase by the amount of misssing days

# Are there differences in activity patterns between weekdays and weekends?

```{r 4}
day <- weekdays(as.Date(im_activity$date))
for (i in 1:NROW(im_activity$steps)){
        if (day[i]=="Saturday"||day[i]=="Sunday"){
                day[i] <- "Weekend"
        } else {
                        day[i] <- "Weekday"
                }
}
wd_activity <- cbind(im_activity,day)
wd <- split(wd_activity,wd_activity$day)
weekday_daily_mean_result <- tapply(wd$Weekday$steps, factor(wd$Weekday$interval),FUN = mean)
weekend_daily_mean_result <- tapply(wd$Weekend$steps, factor(wd$Weekend$interval),FUN = mean)
par(mfrow=c(2,1))
plot(c(1:dim(weekday_daily_mean_result)),weekday_daily_mean_result,
xlab = "time interval index",
ylab = "steps",
main = "weekday",
type = "l")
plot(c(1:dim(weekend_daily_mean_result)),weekend_daily_mean_result,
xlab = "time interval index",
ylab = "steps",
main = "weekend",
type = "l")

```
